Constraints on Assembly Bias from Galaxy Clustering

### 2016-05-26 ms.tex
Minor structural changes to text.

A second noteworthy difference between the present work and that of \citet{zehavi_etal11} is that we 
find many parameters to be notably more poorly constrained. At the lower luminosity thresholds, for example, 
we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
\citet{zehavi_etal11}. We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
$\log (M_0)$ is determined by the prior given in Table~\ref{table:priors}. This is in stark contrast to several of the 
results of \citet{zehavi_etal11}. For example, for the threshold sample with $M_r < -19.5$ ($M_r < -20.5$), 
\citet{zehavi_etal11} quote $\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer 
$\log (M_0) = 11.38^{+0.95}_{-1.57}$ ($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}), 
it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. Therefore, it seems likely 
that the tighter constraints quoted by \citet{zehavi_etal11} must be an error or must be driven by some 
prior that is not clearly specified in their manuscript.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=15.0cm]{Mr19ABTri.pdf}
\caption{
Two-dimensional marginalized constraints on decorated HOD parameters inferred from fits 
to $\wprp(\rp)$ data for the $M_r<-19$ sample. The decorated HOD models include a 
two-parameter model for assembly bias. The HOD parameter $\log (M_0)$ is extremely 
poorly constrained by the data and has been suppressed for clarity. Likewise, as in 
Fig.~\ref{fig:Mr20triangle}, $\sigma_{\log M}$ and $\log (M_{\rm min})$ share a 
narrow degeneracy, so we have suppressed $\sigma_{\log M}$ in order to make 
constraints on other parameters more easily visible.
}
\label{fig:Mr19ABtriangle}
\end{center}
\end{figure*}

>>>>

A second noteworthy difference between the present work and that of \citet{zehavi_etal11} is that we 
find many parameters to be notably more poorly constrained. At the lower luminosity thresholds, for example, 
we constrain $\log (M_{\rm min})$ and $\sigma_{\log M}$ with several times lower precision than 
\citet{zehavi_etal11}. As is evident in Figure~\ref{fig:Mr20triangle}, $\log (M_{\rm min})$ and $\sigma_{\log M}$ 
share a relatively narrow degeneracy. This degeneracy is largely induced by the measured number density of 
the sample. Increasing $\log (M_{\rm min})$ decreases galaxy number density, but this can be compensated by 
an increase in $\sigma_{\log M}$, which places galaxies in a fraction of the considerably more numerous halos 
with masses less than $M_{\rm min}$.

We do not show our constraints on $\log (M_0)$ as they are very poor in all cases, 
with 1-sigma constraints on the order of $\pm \ge 1$~dex for nearly all samples. In several cases, the constraint on 
$\log (M_0)$ is determined by the prior given in Table~\ref{table:priors}. This is in stark contrast to several of the 
results of \citet{zehavi_etal11}. For example, for the threshold sample with $M_r < -19.5$ ($M_r < -20.5$), 
\citet{zehavi_etal11} quote $\log (M_0) = 12.23 \pm 0.17$ ($12.35 \pm 0.24$), whereas we infer 
$\log (M_0) = 11.38^{+0.95}_{-1.57}$ ($11.19^{+0.89}_{-1.39}$). Examining the form of Eq.~(\ref{eq:nsat}), 
it is sensible that the parameter $\log (M_0)$ should be unconstrained at the lower end, because the 
value of $M_0$ does not alter the predicted satellite number once $M_0 \ll M_1$. Therefore, it seems likely 
that the tighter constraints quoted by \citet{zehavi_etal11} must be an error or must be driven by some 
prior that is not clearly specified in their manuscript.

@@

We turn now to a discussion of our parameter inference analysis of projected galaxy clustering 
in Decorated HOD models that include a treatment of galaxy assembly bias. In this work, 
we consider only the simplest model of galaxy assembly bias, introducing only two new 
parameters, $A_{\rm cen}$ and $A_{\rm sat}$, that describe the strength of central galaxy 
and satellite galaxy assembly bias respectively. These parameters are limited to values 
of $-1 \le A_{\rm cen,sat} \le 1$, and $A_{\rm cen,sat}=0$ when there is no galaxy assembly bias. 
In this work, we use halo concentration as our secondary halo property, so $A_{\rm cen,sat}=1$ 
($A_{\rm cen,sat}=-1$) means that the mean number of galaxies per halo is maximally 
correlated (anti-correlated) with halo concentration. The model and its implementation 
in {\tt halotools} is discussed further in Section~\ref{subsection:decorated} above.

The one-dimensional marginalized constraints on all parameters form these analyses 
are given in the lowest row of each luminosity threshold grouping in Table~\ref{table:parameters}. 
In cases where the posterior on a parameter is monotonic within the physical parameter 
range, we quote an upper or lower limit on the parameter.

Examples of our fits are given in the right-hand panels of Figure~\ref{fig:Mr19samples}, 
Figure~\ref{fig:Mr20samples}, and Figure~\ref{fig:Mr21samples}. The general trend that 
can be gleaned from these figures is that introducing assembly bias improves the ability 
of the predicted two-point functions to match the measured two-point functions across the 
transition form the one-halo (highly nonlinear) to two-halo (nearly linear) regimes near $\rp \sim 2\, h^{-1}{\mathrm{Mpc}}$. 
Visually, these differences appear to be small; however, Table~\ref{table:parameters} shows that 
they are statistically important.

%------------------------------------------------------------------------------------------------
\begin{figure*}
\begin{center}
\includegraphics[width=15.0cm]{Mr19ABTri.pdf}
\caption{
Two-dimensional marginalized constraints on decorated HOD parameters inferred from fits 
to $\wprp(\rp)$ data for the $M_r<-19$ sample. The contours and histograms along the diagonal 
panels are as in Fig.~\ref{fig:Mr20triangle}. The decorated HOD models include a 
two-parameter model for assembly bias. The HOD parameter $\log (M_0)$ is extremely 
poorly constrained by the data and has been suppressed for clarity. Likewise, as in 
Fig.~\ref{fig:Mr20triangle}, $\sigma_{\log M}$ and $\log (M_{\rm min})$ share a 
narrow degeneracy, so we have suppressed $\sigma_{\log M}$ in order to make 
constraints on other parameters more easily visible.
}
\label{fig:Mr19ABtriangle}
\end{center}
\end{figure*}
%----------------------------------------------------------------------------------------------
